03-modeling

### 2018-07-13 02_scripts/035_all-plots/03-modeling_all.Rmd
- start intro - update results - update data and sutdy area

```{r}
lrn_xgboost <- makeLearner("regr.xgboost",
                   par.vals = list(
                     objective = "reg:linear",
                     eval_metric = "error",
                     eta = 0.1
                   ))
```

```{r}
ps_xgboost = makeParamSet(
  makeDiscreteParam("nrounds", values = c(10, 100, 1000, 10000)),
  makeNumericParam("colsample_bytree", lower=0.1, upper=1),
  makeNumericParam("subsample", lower=0.1, upper=1),
  makeIntegerParam("max_depth", lower=1, upper=785),
  makeNumericParam("gamma", lower=0, upper=20)
)
```

```{r}
ctrl = makeMBOControl(propose.points = 1L)
ctrl = setMBOControlTermination(ctrl, iters = 70L)
ctrl = setMBOControlInfill(ctrl, crit = crit.ei)
ctrl = setMBOControlMultiPoint(ctrl, method = "cl", cl.lie = min)
tune.ctrl = makeTuneControlMBO(mbo.control = ctrl,
                               mbo.design = generateDesign(n = 30, par.set = ps_xgboost))
inner <- makeResampleDesc("Blocking")
```

@@

@@

>>>>

```{r}
lrn_xgboost <- makeLearner("regr.xgboost",
                   par.vals = list(
                     objective = "reg:linear",
                     eval_metric = "error"
                   ))
```

```{r}
ps_xgboost <- makeParamSet(
  makeIntegerParam("nrounds", lower = 0, upper = 600),
  makeNumericParam("colsample_bytree", lower = 0.3, upper = 0.7),
  makeNumericParam("subsample", lower = 0.25, upper = 1),
  makeIntegerParam("max_depth", lower = 1, upper = 10),
  makeNumericParam("gamma", lower = 0, upper = 10),
  makeNumericParam("eta", lower = 0.001, upper = 0.6),
  makeNumericParam("min_child_weight", lower = 0, upper = 20)
)
```

```{r}
ctrl = makeMBOControl(propose.points = 1L)
ctrl = setMBOControlTermination(ctrl, iters = 20L)
ctrl = setMBOControlInfill(ctrl, crit = crit.ei)
ctrl = setMBOControlMultiPoint(ctrl, method = "cl", cl.lie = min)
tune.ctrl = makeTuneControlMBO(mbo.control = ctrl,
                               mbo.design = generateDesign(n = 30, par.set = ps_xgboost))
# tune.ctrl = makeTuneControlRandom(maxit = 50)
inner <- makeResampleDesc("Blocking")
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", cpus = 4, level = "mlr.resample",
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
resa_svm <- mlr::resample(tune_wrapper, task,
                          resampling = outer, extract = getTuneResult,
                          show.info = TRUE, measures = list(rmse))
# resa_svm <- mlr::resample(lrn_xgboost, task,
#                           resampling = outer, 
#                           show.info = TRUE, measures = list(rmse))

@@

### RF

```{r}
# RF
ps_rf <- makeParamSet(
  makeIntegerParam("mtry", lower = 1, upper = 3000),
  makeIntegerParam("min.node.size", lower = 1, upper = 10),
  makeNumericParam("sample.fraction", lower = 0.2, upper = 0.9)
)
ctrl <- makeMBOControl(propose.points = 1L)
ctrl <- setMBOControlTermination(ctrl, iters = 20L)
ctrl <- setMBOControlInfill(ctrl, crit = crit.ei)
ctrl <- setMBOControlMultiPoint(ctrl, method = "cl", cl.lie = min)
tune.ctrl <- makeTuneControlMBO(
  mbo.control = ctrl,
  mbo.design = generateDesign(n = 30, par.set = ps_rf)
)
inner <- makeResampleDesc("Blocking")

tune_wrapper_rf <- makeTuneWrapper(makeLearner("regr.ranger"),
                                   resampling = inner, par.set = ps_rf,
                                   control = tune.ctrl, show.info = TRUE,
                                   measures = list(rmse)
)
```

```{r}
library(parallelMap)
parallelStart(mode = "multicore", cpus = 40, level = "mlrMBO.feval",
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
resa_svm <- mlr::resample(tune_wrapper_rf, task,
                          resampling = outer, extract = getTuneResult,
                          show.info = TRUE, measures = list(rmse))

parallelStop()
saveRDS(resa_svm, "/data/patrick/mod/hyperspectral/spcv/all_plots_rf_blocking.rda")
```
